% This file was derived from a template created by Joshua Ryan Smith 
% (joshua.r.smith@gmail.com). The template can be found in the git repo at:
% http://github.com/jrsmith3/latex_template

\documentclass[letterpaper,12pt]{article}

% Document graphics and formatting
% ================================
\usepackage{graphicx}
\graphicspath{{../pics/}}
\usepackage{showkeys}
% \usepackage{endfloat}
% \usepackage{url}
\usepackage{amsmath}
\usepackage[version=3]{mhchem}

% Document metadata
% =================
\newcommand{\Title}{Analytic solution to the incomplete Bose-Einstein integral}
\newcommand{\AuthorName}{Joshua Ryan Smith}
\newcommand{\AuthorEmail}{joshua.smith133.ctr@mail.mil}

\usepackage[pdftex,colorlinks=true,hidelinks]{hyperref}
\hypersetup{
pdftitle={\Title},
pdfauthor={\AuthorName (\AuthorEmail)},
pdfsubject={},
pdfkeywords={},
pdfcreator={pdfTeX}
}

% Define polylogarithm notation for reuse
% =======================================
\newcommand{\Li}{\textrm{Li}}

% Label index
% ===========
% eq:
% --
% 00,01,02,03,04,05,06,07,08,09,
% 10,11,12,13,14,15,16,17,18,19,
% 20,21,22,23,24,25,26,27,28,29,
% 30,31,32,33,34,35,36,37,38,39,
% 40,41,42,43,44,45,46,47,48,49,
% 50,51,
% 
% fig
% ---
%
% sec
% ---
%
% tab
% ---

\title{\Title}
\author{\AuthorName}

\begin{document}

\maketitle


\begin{abstract}
The canonical incomplete Bose-Einstein integral is expressed in terms of a finite sum of polylogarithm functions.
\end{abstract}


\section{Introduction}
Computing photon energy and particle fluxes using the imcomplete Bose-Einstein integral is central to calculating the efficiency of efficiency limits of solar cells in the detailed balance limit \cite{10.1063/1.1736034}. This integral also appears in the calculation of the photo-enhanced thermoelectron emission (PETE) from materials \cite{10.1038/nmat2814}. Herein a solution to the incomplete Bose-Einstein integral is derived in terms of the polylogarithm function for the case of integer values of the exponent. The polylogarithm has the attractive property of rapid convergence via direct summation for small values of the argument \cite{http://academic.reed.edu/physics/faculty/crandall/papers/Polylog}; a property that will be exploited in this case to rapidly and precisely calculate the numerical value of the incomplete Bose-Einstein integral.


\section{Calculation}
Levy and Honsberg \cite{10.1016/j.sse.2006.06.017} give the incomplete Bose-Einstein integral as in Eq. \ref{eq:26}

\begin{equation} \label{eq:26}
F_{m}(E_{A},E_{B},T,\mu) = \frac{2 \pi}{h^{3}c^{2}} \int_{E_{A}}^{E_{B}} E^{m} \frac{1}{\exp \left( \frac{E - \mu}{kT} \right) - 1} dE 
\end{equation}


\noindent for conditions $\mu < E_{A}$ and $0 < E_{A} < E_{B}$; the value of $F_{m}$ is zero when the previous conditions are not met. The quantities $E_{A}$ and $E_{B}$ are the lower and upper limits of the photon emission, respectively, $\mu$ is the equilibrium chemical potential of the radiation, $T$ is the absolute temperature of the solid, $c$ is the speed of light, $h$ is Planck's constant, and $k$ is Boltzmann's constant. The quantity $m$ takes the value of 2 or 3 for photon number flux and photon energy flux, respectively.


% Shockly and Quiesser \cite{10.1063/1.1736034} give an expression for $Q(\nu_{g}, T)$; the number of photons of frequency greater than $\nu_{g}$ leaving a material per unit area per unit time for blackbody radiation of temperature $T$. This expression is represented in Eq. \ref{eq:00}

% \begin{equation} \label{eq:00}
% Q(\nu_{g}, T) = \frac{2\pi}{c^{2}} \int_{\nu_{g}}^{\infty} \frac{\nu^{2}}{\exp\left( \frac{h \nu}{kT} \right) - 1} d\nu
% \end{equation}

% \noindent where $c$ is the speed of light in vacuum, $h$ is Planck's constant, $k$ is Boltzmann's constant, and $\nu$ is the frequency of a photon.

In the following derivation, the incomplete Bose-Einstein integral given in Eq. \ref{eq:26} will be expressed in terms of the polylogarithm function of integer order and real argument. The polylogarithm is defined in Eq. \ref{eq:22}. First, the upper incomplete Bose-Einstein integral will be calculated -- that is, with limits from $E_{A}$ to $\infty$. The resulting expression will be used to calculate the incomplete Bose-Einstein integral given in Eq. \ref{eq:26} from $E_{A}$ to $E_{B}$.

\begin{equation} \label{eq:22}
\Li_{s}(z) = \sum_{n = 1}^{\infty} \frac{z^{n}}{n^{s}}, \qquad |z| < 1
\end{equation}

\subsection{Upper-incomplete Bose-Einstein integral}
Consider the upper incomplete Bose-Einstein integral given in Eq. \ref{eq:27} with the variables changed such that

\begin{equation} \label{eq:28}
x \equiv \frac{E}{kT}
\end{equation}

\noindent and

\begin{equation} \label{eq:29}
u \equiv \frac{\mu}{kT}
\end{equation}

\noindent so

\begin{align} \label{eq:27}
F_{m}(E_{A},\infty,T,\mu) &= \frac{2 \pi}{h^{3}c^{2}} \int_{E_{A}}^{\infty} E^{m} \frac{1}{\exp \left( \frac{E - \mu}{kT} \right) - 1} dE \nonumber \\
 &= \frac{2 \pi (kT)^{m+1}}{h^{3}c^{2}} \int_{x_{A}}^{\infty} x^{m} \frac{1}{\exp(x-u) - 1} dx
\end{align}

\noindent where $x_{A} = E_{A}/kT$.

The exponential term can be factored from the denominator of the integrand of Eq. \ref{eq:27} to yield

\begin{equation} \label{eq:30}
F_{m}(\ldots) = \frac{2 \pi (kT)^{m+1}}{h^{3}c^{2}} \int_{x_{A}}^{\infty} x^{m} \frac{\exp(u-x)}{1 - \exp(u-x)} dx
\end{equation}


The geometric series can be rearranged in order to replace the fractional term of the integrand of Eq. \ref{eq:30} with a sum. The geometric series is given in Eq. \ref{eq:03}

\begin{equation} \label{eq:03}
\frac{1}{1-r} = \sum_{n = 0}^{\infty} r^{n}, \qquad |r| < 1
\end{equation}

\noindent Moving the first term of the sum to the left hand side and simplifying yields

\begin{equation} \label{eq:04}
\frac{r}{1-r} = \sum_{n = 1}^{\infty} r^{n}, \qquad |r| < 1
\end{equation}


Note that $\exp(u-x) < 1$ since $u < x$ for all values of $x$ over the entire range of integration as specified in Eq. \ref{eq:27}; substituting this exponentiation for $r$ into Eq. \ref{eq:04} yields

\begin{align} \label{eq:06}
\frac{\exp(u-x)}{1 - \exp(u-x)} &= \sum_{n = 1}^{\infty} \exp(u-x)^{n} \nonumber \\
 &= \sum_{n = 1}^{\infty} \exp(nu) \exp(-nx)
\end{align}


The sum from Eq. \ref{eq:06} can be substituted into the expression in Eq. \ref{eq:30} to yield

\begin{align} \label{eq:07}
F_{m}(\ldots) &= \frac{2\pi (kT)^{m+1}}{h^{3} c^{2}} \int_{x_{A}}^{\infty} x^{m} \frac{\exp(u-x)}{1 - \exp(u-x)} dx \nonumber \\
 &= \frac{2\pi (kT)^{m+1}}{h^{3} c^{2}} \int_{x_{A}}^{\infty} x^{m} \sum_{n = 1}^{\infty} \exp(nu) \exp(-nx) dx \nonumber \\
 &= \frac{2\pi (kT)^{m+1}}{h^{3} c^{2}} \sum_{n = 1}^{\infty} \exp(nu) \int_{x_{A}}^{\infty} x^{m} \exp(-nx) dx
\end{align}

Consider a general term in the series given in Eq. \ref{eq:07}

\begin{equation} \label{eq:08}
\int_{x_{A}}^{\infty} x^{m} \exp(-nx) dx
\end{equation}

\noindent Note

\begin{equation} \label{eq:09}
\int_{0}^{\infty} x^{m} \exp(-nx) dx = \int_{x_{A}}^{\infty} x^{m} \exp(-nx) dx + \int_{0}^{x_{A}} x^{m} \exp(-nx) dx
\end{equation}

\noindent so

\begin{equation} \label{eq:10}
\int_{x_{A}}^{\infty} x^{m} \exp(-nx) dx = \int_{0}^{\infty} x^{m} \exp(-nx) dx - \int_{0}^{x_{A}} x^{m} \exp(-nx) dx
\end{equation}

\noindent The integral from 0 to $\infty$ can easily be evaluated -- \emph{cf}. integral 641 \cite{9780849324796}.

\begin{equation} \label{eq:11}
\int_{0}^{\infty} x^{m} \exp(-nx) dx = \frac{m!}{n^{m+1}}
\end{equation}

Now consider the integral from 0 to $x_{A}$ and change variable so the integral is evaluated from 0 to 1.

\begin{equation} \label{eq:12}
y \equiv \frac{x}{x_{A}}
\end{equation}

\begin{align} \label{eq:13}
\int_{0}^{x_{A}} x^{m} \exp(-nx) dx &= \int_{0}^{1} (x_{A}y)^{m} \exp(-nx_{A}y) x_{A} dy \nonumber \\
 &= x_{A}^{m+1} \int_{0}^{1} y^{m} \exp(-nx_{A}y) dy
\end{align}

\noindent Using integral 650 of \cite{9780849324796}, Eq. \ref{eq:13} becomes

\begin{equation} \label{eq:15}
\int_{0}^{x_{A}} x^{m} \exp(-nx) dx = \frac{m!}{n^{m+1}} \left(1 - \exp(-n x_{A}) \sum_{j = 0}^{m} \frac{(n x_{A})^{j}}{j!} \right) 
\end{equation}

Substituting Eqs. \ref{eq:11} and \ref{eq:15} into Eq. \ref{eq:10} yields

\begin{equation} \label{eq:31}
\int_{x_{A}}^{\infty} x^{m} \exp(-nx) dx = \frac{m!}{n^{m+1}} \exp(-n x_{A}) \sum_{j = 0}^{m} \frac{(n x_{A})^{j}}{j!}
\end{equation}

which can be substituted into Eq. \ref{eq:07} to yield

\begin{align} \label{eq:32}
F_{m}(\ldots) &= \frac{2\pi (kT)^{m+1}}{h^{3} c^{2}} \sum_{n = 1}^{\infty} \exp(nu) \int_{x_{A}}^{\infty} x^{m} \exp(-nx) dx \nonumber \\
 &= \frac{2\pi (kT)^{m+1}}{h^{3} c^{2}} \sum_{n = 1}^{\infty} \exp(nu) \frac{m!}{n^{m+1}} \exp(-n x_{A}) \sum_{j = 0}^{m} \frac{(n x_{A})^{j}}{j!} \nonumber \\
 &= \frac{2\pi m! (kT)^{m+1}}{h^{3} c^{2}} \sum_{n = 1}^{\infty} \exp(nu) \sum_{j = 0}^{m} \frac{x_{A}^{j}}{j!} \frac{\exp(-n x_{A})}{n^{m-j+1}} \nonumber \\
 &= \frac{2\pi m! (kT)^{m+1}}{h^{3} c^{2}} \sum_{n = 1}^{\infty} \exp(nu) \sum_{s = 1}^{m+1} \frac{x_{A}^{m-s+1}}{(m-s+1)!} \frac{\exp(-n x_{A})}{n^{s}} \nonumber \\
 &= \frac{2\pi m! (kT)^{m+1}}{h^{3} c^{2}} \sum_{s = 1}^{m+1} \frac{x_{A}^{m-s+1}}{(m-s+1)!} \sum_{n = 1}^{\infty} \frac{\exp(nu-n x_{A})}{n^{s}} \nonumber \\
 &= \frac{2\pi m! (kT)^{m+1}}{h^{3} c^{2}} \sum_{s = 1}^{m+1} \frac{x_{A}^{m-s+1}}{(m-s+1)!} \sum_{n = 1}^{\infty} \frac{\exp(u-x_{A})^{n}}{n^{s}} \nonumber \\
 &= \frac{2\pi m! (kT)^{m+1}}{h^{3} c^{2}} \sum_{s = 1}^{m+1} \frac{x_{A}^{m-s+1}}{(m-s+1)!} \Li_{s} \left( \exp(u-x_{A}) \right)
\end{align}

\noindent after re-indexing the sum over $j$ to one over $s$ where $s = m - j + 1$. It is appropriate to replace the sum with the polylogarithm function as given in Eq. \ref{eq:22} since, again, $u < x$ and therefore $\exp(u-x) < 1$. Thus, the upper incomplete Bose-Einstein integral has been expressed in terms of a finite sum of polylogarithm functions of integer order and real argument.

\subsection{Incomplete Bose-Einstein integral}
The incomplete Bose-Einstein integral given in Eq. \ref{eq:26} can be expressed as a difference of two upper-incomplete Bose-Einstein integrals evaluated at different limits.

\begin{align} \label{eq:33}
F_{m}&(E_{A}, E_{B}, T, \mu) = F_{m}(E_{A}, \infty, T, \mu) - F_{m}(E_{B}, \infty, T, \mu) \nonumber \\
 &= \frac{2\pi m! (kT)^{m+1}}{h^{3} c^{2}} \sum_{s = 1}^{m+1} \frac{1}{(m-s+1)!} \left( x_{A}^{m-s+1} \Li_{s} \left( \exp(u-x_{A}) \right) - x_{B}^{m-s+1} \Li_{s} \left( \exp(u-x_{B}) \right)
\right)
\end{align}

\noindent where $x_{B} = E_{B}/kT$.


\section{Uncertainty analysis}
The polylogarithm can be written in terms of an infinite series as in Eq. \ref{eq:22}. One algorithm to approximate the value of the polylogarithm is to simply compute and sum the first $l$ terms of the series and stop when the remainder of the series (the terms from $l+1$ and greater) is accepatably small.

Consider the polylogarithm written as the sum of two terms, the partial sum of the first $l$ terms and the remainder, as in Eq. \ref{eq:34}

\begin{equation} \label{eq:34}
\Li_{s}(z) = \Li_{s,l}^{lo}(z) + \Li_{s,l}^{high}(z), \qquad |z| < 1
\end{equation}

\noindent where the partial sum is

\begin{equation} \label{eq:35}
\Li_{s,l}^{lo}(z) = \sum_{n = 1}^{l} \frac{z^{n}}{n^{s}}, \qquad |z| < 1
\end{equation}

\noindent and the remainder is

\begin{equation} \label{eq:36}
\Li_{s,l}^{high}(z) = \sum_{n = l + 1}^{\infty} \frac{z^{n}}{n^{s}}, \qquad |z| < 1
\end{equation}


Terms should be computed and summed until the ratio

\begin{equation} \label{eq:37}
U = \frac{\Li_{s,l}^{lo}(z)}{\Li_{s,l}^{high}(z)}
\end{equation}

\noindent becomes large. The magnitude of this ratio determines the significance of the digits given in the decimal representation of $\Li_{s,l}^{lo}(z)$. For example, if the value of $U$ is on the order of $1 \times 10^{10}$, the remainder will only change digits in the $1 \times 10^{11}$ place and below in the decimal representation of the approximation to $\Li_{s}(z)$. Practically speaking, there is no need to compute the value of $\Li_{s}(z)$ to a higher precision than the precision to which the physical constants of Eq. \ref{eq:32} are known. The value of the uncertainty ratio $U$ can be bounded by bounding both the partial sum and remainder of the polylogarithm.

The remainder can be bounded above by a (hyper?)-geometric series. Consider the remainder 

\begin{align} \label{eq:38}
\Li_{s,l}^{high}(z) &= \sum_{n = l + 1}^{\infty} \frac{z^{n}}{n^{s}} \\
 &= \frac{z^{l+1}}{(l+1)^{s}} + \frac{z^{l+2}}{(l+2)^{s}} + \frac{z^{l+3}}{(l+3)^{s}} + ...
\end{align}

\noindent This series is bounded above by the corresponding terms of the geometric series

\begin{align} \label{eq:39}
G_{l}^{high}(z) &= \sum_{n = l + 1}^{\infty} z^{n} \\
 &= z^{l+1} + z^{l+2} + z^{l+3} + ...
\end{align}

\noindent This upper bound can be further lowered by dividing through by $(l + 1)^{s}$

\begin{align} \label{eq:40}
\frac{G_{l}^{high}(z)}{(l+1)^{s}} = 
\frac{z^{l+1}}{(l+1)^{s}} + \frac{z^{l+2}}{(l+1)^{s}} + \frac{z^{l+3}}{(l+1)^{s}} + ...
\end{align}

It is clear from the following table that the terms from the remainder of the polylogarithm sum are less than the corresponding terms from the reduced geometric series 

\begin{tabular}{ccc}
$n$ & $\Li_{s,l}^{high}(z)$ & $\frac{G_{l}^{high}(z)}{(l+1)^{s}}$ \\
\hline
$l+1$ & $\frac{z^{l+1}}{(l+1)^{s}}$ & $\frac{z^{l+1}}{(l+1)^{s}}$ \\
$l+2$ & $\frac{z^{l+2}}{(l+2)^{s}}$ & $\frac{z^{l+2}}{(l+1)^{s}}$ \\
$l+3$ & $\frac{z^{l+3}}{(l+3)^{s}}$ & $\frac{z^{l+3}}{(l+1)^{s}}$ \\
... & ... & ... \\
\end{tabular}

\noindent therefore,

\begin{equation} \label{eq:41}
\Li_{s,l}^{high}(z) < \frac{G_{l}^{high}(z)}{(l+1)^{s}}
\end{equation}

In addition, the partial sum of the lower terms of the polylogarithm series can be bounded below by the corresponding terms of a partial (hyper?)geometric series. Consider the partial sum of the polylogarithm series

\begin{align} \label{eq:42}
\Li_{s,l}^{lo}(z) &= \sum_{n = 1}^{l} \frac{z^{n}}{n^{s}} \\
 &= z + \frac{z^{2}}{2^{s}} + \frac{z^{3}}{3^{s}} + ... + \frac{z^{l}}{l^{s}}
\end{align}

\noindent Consider also the corresponding terms of the geometric series

\begin{align} \label{eq:43}
G_{l}^{lo}(z) &= \sum_{n = 1}^{l} z^{n} \\
 &= z + z^{2} + z^{3} + ... + z^{l}
\end{align}

\noindent Dividing the partial sum of the lower tems of the geometric series by $(l+1)^{s}$ yields

\begin{equation} \label{eq:44}
\frac{G_{l}^{lo}(z)}{(l+1)^{s}} = \frac{z}{(l+1)^{s}} + \frac{z^{2}}{(l+1)^{s}} + \frac{z^{3}}{(l+1)^{s}} + ... + \frac{z^{l}}{(l+1)^{s}}
\end{equation}

Comparing the terms from the two partial sums it is clear that each term from the polylogarithm series is greater than or equal to the corresponding term of the geometric series.

\begin{tabular}{ccc}
$n$ & $\Li_{s,l}^{lo}(z)$ & $\frac{G_{l}^{lo}(z)}{(l+1)^{s}}$ \\
\hline
$1$ & $z$ & $\frac{z}{(l+1)^{s}}$ \\
$2$ & $\frac{z^{2}}{2^{s}}$ & $\frac{z^{2}}{(l+1)^{s}}$ \\
$3$ & $\frac{z^{3}}{3^{s}}$ & $\frac{z^{3}}{(l+1)^{s}}$ \\
... & ... & ... \\
$l$ & $\frac{z^{l}}{l^{s}}$ & $\frac{z^{l}}{(l+1)^{s}}$ \\
\end{tabular}

\noindent Thus

\begin{equation} \label{eq:45}
\Li_{s,l}^{lo}(z) > \frac{G_{l}^{lo}(z)}{(l+1)^{s}}
\end{equation}

Noting the inequalities of Eqs. \ref{eq:41} and \ref{eq:45}, the uncertainity ratio $U$ is bounded by

\begin{equation} \label{eq:46}
U > \frac{G_{l}^{lo}(z)}{G_{l}^{high}(z)}
\end{equation}

\noindent which is to say that the uncertainty ratio of the polylogarithm will be better (higher) than the uncertainty ratio of the partial sum of a geometric series to its remainder. Expressions for the numerator and denominator of Eq. \ref{eq:46} are easily found and Eq. \ref{eq:46} can be simplified to

\begin{equation} \label{eq:47}
U > z^{-l} - 1
\end{equation}

\noindent Therefore, an arbitrary precision $U$ can be selected and the number of terms $l$ of the polylogarithm partial sum to achieve that precision can be determined for a given value of $z$

\begin{align} \label{eq:48}
l &= -\frac{\log(U+ 1)}{\log(z)} \\
 &\approx -\frac{\log(U)}{\log(z)}
\end{align}

\noindent where $\log$ is the logarithm base 10. It is clear from Eq. \ref{eq:47} that high precision (high $U$) can be achieved from few terms (low $l$) of the polylogarithm partial sum approximation when the argument $z$ is small. Conversely, as the value of $z$ approachs unity, more terms in the polylogarithm partial sum approximation (high $l$) are required to achieve high precision (high $U$). Fig. \ref{} depicts the uncertainty ratio vs. teh number of terms in the partial sum approximation of the polylogarithm for a family of curves corresponding to different values of argument $z$.

\subsection{Practical limit of precision}
Practically speaking, no more than (VALUE) terms of the partial sum approximation will ever be required to be calculated because the precision of the value of the partial sum approximation is limited by the precision of the argument $z$. In the case examined by this paper, 

\begin{equation} \label{eq:49}
z = \exp \left( \frac{\mu - E_{A}}{kT} \right)
\end{equation}

Analyzing the uncertainty propagation following Taylor \cite{9780935702422}, the uncertainty, $\delta z$, in $z$ is

\begin{equation} \label{eq:50}
\delta z = \exp \left( \frac{\mu - E_{A}}{kT} \right) \left[\frac{(\delta \mu)^{2} + (\delta E_{A})^{2}}{(\mu - E_{A})^{2}} + \left( \frac{\delta k}{k} \right)^{2} + \left( \frac{\delta T}{T} \right)^{2} \right]^{1/2}
\end{equation}

\noindent Therefore the precision of $z$ is capped by the least precise quantity among $\mu$, $E_{A}$, $T$, and $k$. Of these quantities, Boltzmann's constant will almost certainly be the most precise. To determine the maximum number of terms required in the partial sum approximation of the polylogarithm, assume $\mu$, $E_{A}$, and $T$ are all known to absolute precision and therefore $k$ is the limiting quantity. According to NIST \cite{}, $k$ is known to (VALUE) precision. Therefore, Eq. \ref{eq:50} reduces to

\begin{equation} \label{eq:51}
\delta z = \exp \left( \frac{\mu - E_{A}}{kT} \right) \left| \frac{\delta k}{k} \right|
\end{equation}

\noindent and (VALUE) is the largest unambiguous value $z$ can acquire.


\section{Results}
The incomplete Bose-Einstein integral was implemented in python as a module \cite{}. The output of the calculation was compared against previously reported values of the efficiencies of a single-junction solar cells. Shockley and Queisser \cite{10.1063/1.1736034} report that the maximum efficiency of a single-junction solar cell is 44\% and has a bandgap of 1.1eV assuming a solar temperature of 6000K. Using the derivation presented in this paper, an efficiency of (VALUE) was obtained under identical conditions in good agreement with Shockley and Queisser. In addition, the efficiency vs. bandgap was calculated using the derivation presented in this paper and the result is depicted in Fig. \ref{}; this figure matches Shockley and Queisser's Fig. 3.

DeVos \cite{9780198513926} reports a maximum efficiency of 40.8\% for a single-junction solar cell of bandgap 1.15eV illuminated by fully concentrated sunlight of temperature 5762K. An efficiency of (VALUE) was calculated using the derivation described in this paper under identical conditions.


\section{Colophon}
The model was implemented as a module written in python. Revision (VALUE) \cite{} of the software implementing the model was used for the calculations in this manuscript along with sympy version (VALUE), numpy version (VALUE), matplotlib version (VALUE), and python version (VALUE) -- all included with Continuum Analytics's Anaconda distribution version (VALUE).  The code was executed on a MacBook Air model A1466 running OS X (VALUE), Darwin kernel version (VALUE) with a 2GHz Intel core i7 and 8GB 1600 MHz DDR3 memory.


\section{Acknowledgements}
The author would like to express extreme gratitude to the staff of the Research Library of the Army Research Laboratory Adelphi Laboratory Center, particularly Nancy Faget, James, Gary, Louise McGovern, and the other lady: thank you very much for tracking down all of the books and papers I needed to write this manuscript. Many thanks also to Sasha Wood for tips on how to bound the uncertainty of the polylogarithm function.

Research was sponsored by the Army Research Laboratory and was accomplished under Cooperative Agreement Number W911NF-12-2-0019. The views and conclusions contained in this document are those of the authors and should not be interpreted as representing the official policies, either expressed or implied, of the Army Research Laboratory or the U.S. Government. The U.S. Government is authorized to reproduce and distribute reprints for Government purposes notwithstanding any copyright notation herein.


\bibliographystyle{nar}
\bibliography{bib}
\end{document}
